Higgs Assisted Razor Search for Higgsinos at a 100 TeV $pp$ Collider

### 2019-12-17 main.tex
Removed duplicate references, added note about minimum of 3 events

The existence of dark matter provides unambiguous evidence of new physics
beyond the Standard Model (SM) of particle physics. Indeed, given that there is
far more dark matter in the Universe than there is baryonic matter, determining
its precise nature is one of the most exciting challenges in particle physics
today.  One promising group of candidates for dark matter is the class of stable
particles known as weakly interacting massive particles (WIMPs). These
particles arise naturally in many extensions of the SM that are motivated by
the need to stabilize the electroweak scale. One of the most heavily studied extensions
is the Minimal Supersymmetric Standard Model (MSSM), which predicts a
`supersymmetric partner', or \emph{superpartner}, for each SM
particle\footnote{For a detailed review of the MSSM, see Ref.
\cite{Martin:1997ns}.}. In the MSSM with \emph{R}-parity conservation, the
lightest supersymmetric partner (LSP) is predicted to be absolutely stable,
making it a good candidate for dark matter. The identity of the LSP is
determined by the mass hierarchy of the superpartners, which in turn depends on
the mechanism of supersymmetry breaking.  However, taking into account experimental
constraints and phenomenological considerations, \st{the lightest of the MSSM
particles known as the neutralinos emerges as the most attractive candidate
for the LSP}
\Shufang{neutralino LSP emerges as the most attractive candidate for WIMP dark matter.}~\cite{Bertone:2004pz}.

 % Why go beyond the MSSM?
Though a natural MSSM spectrum has the potential to tame the hierarchy problem,
it is under siege from recent data from the Large Hadron Collider (LHC)
\cite{Aaboud:2018ujj, Sirunyan:2018vjp}.  A compelling alternative scenario
comes in the form of split supersymmetry (split SUSY) \cite{Wells:2003tf,
ArkaniHamed:2004yi, Giudice:2004tc}. In this scenario, the lightest
superpartners are the fermionic ones, on the scale of 1-10 TeV, while the
scalar superpartners can be much heavier, on the scale of 100 - 1000 TeV. In
exchange for accepting some level of fine-tuning, we obtain numerous benefits,
including the suppression of flavor-changing neutral currents and greater
compatibility with data from CP-violation experiments.  The low lying fermionic
superpartners consist of neutralinos and charginos (collectively known as
electroweakinos), and gluinos. The current LHC search limits on gluinos are
already around 2 TeV for prompt decay and 2.5 TeV for disappearing track
searches~\cite{CMS-PAS-SUS-19-005}. \Shufang{The limits on electroweakinos with heavy scalar superparticles, however, are still relatively weak: between 150 GeV $-$ 1.0 TeV, depending on the neutralino/chargino species, decay modes, and their mass splittings~\cite{ATL-PHYS-PUB-2019-022, Sirunyan:2017lae,Sirunyan:2018ubx,  Aaboud:2018htj,Aaboud:2018zeb, 
Aad:2019qnd,Aad:2019vvf,Aad:2019vnb,Aaboud:2018ngk,Aaboud:2018sua,Aaboud:2018jiw,Aaboud:2017leg,Aaboud:2017mpt,Aaboud:2017nhr}.  In this paper, we will focus on the discovery potential of the
neutralinos and charginos at a 100 TeV $pp$ collider. }
{\bf Can not find Ref. 9}

@@

\Shufang{
The optimal search strategy for finding electroweakinos is highly dependent on
their mass spectra \cite{Han:2013kza}. There are phenomenological collider studies on
finding electroweakinos with a small mass splitting of about 0.1 $-$ 50 GeV at the LHC~\cite{Giudice:2010wb, Gori:2013ala, Han:2013usa, Schwaller:2013baa, Baer:2014cua, Han:2014kaa} and 
at a 100 TeV $pp$  collider~\cite{Low:2014cba, Bramante:2014tba,
  Berlin:2015aba, Cirelli:2014dsa, Mahbubani:2017gjh, Mahbubani:2018tin,
Fukuda:2017jmk, Saito:2019rtg,Han:2018wus}.
For 100 TeV $pp$ collider with $30\ \text{ab}^{-1}$ of data, disappearing track search can discover Wino (Higgsino) LSP with mass up to about 4.7 TeV (1 TeV)~\cite{Low:2014cba,Cirelli:2014dsa,Mahbubani:2017gjh,Saito:2019rtg,Han:2018wus}.   The discovery reach from Monojet, mono-$Z$, mono-photon search is weaker: about 1 TeV (600 GeV) for Wino (Higgsino)~\cite{Low:2014cba,Cirelli:2014dsa,Mahbubani:2018tin,Han:2018wus}.  For mass splittings of about 20-30 GeV between low-lying neutralinos and charginos, soft lepton plus missing $E_T$ signal can be used~\cite{Low:2014cba,Bramante:2014tba}.  In addition, Weak boson fusion process can discover a Wino (Higgsino) up to about 1 TeV (530 GeV)~\cite{Cirelli:2014dsa, Berlin:2015aba}.  Note, however,  that in certain
scenarios, light Higgsinos between 75 $-$ 100 GeV are still viable, evading LEP and LHC
constraints \cite{Egana-Ugrinovic:2018roi}.}

@@

Searches for pair produced nearly mass-degenerate Higgsinos  have been
performed at ATLAS and CMS for various decay topologies
\cite{Aaboud:2018htj,Sirunyan:2018ubx,Aaboud:2018zeb}.  
For neutralino-chargino pair production with \emph{WZ} and \emph{Wh} topologies, the 95\%
C.L. exclusion limits are about 650 GeV, 490 GeV, and 535 GeV for \emph{WZ}, \emph{Wh} and an equal mixture of \emph{WZ}+\emph{Wh} topology, with the strongest limits coming from
the multi-lepton searches.  For neutralino pair production with \emph{ZZ, Zh}, and \emph{hh} topologies\footnote{While such searches assume a gravitino LSP with Higgsino NLSPs, the limits are still relevant for our Higgsino NLSPs - Bino
LSP scenario.}, the limits are about 650 $-$ 750 GeV via multi-lepton or
multi-$b$ jets searches, depending on the decay branching fractions of the Higgsino NLSPs.

@@

Table \ref{tab:cc_cutflowtable} shows the cut efficiencies for a representative
signal benchmark point with $\mu =$ 1 TeV and $M_1$ = 25 GeV.   The
cross-sections of the backgrounds are obtained from MadEvent after performing the MLM matching procedure. Their small size reflects
the $m_{\ell\ell}$ and $\slashed{E}_T$ cuts we imposed at the parton level. For all
the benchmark points, we require a minimum of 3 signal events left over after
cuts. We can see that, after applying our cuts, $tbW$ remains as the
dominant backgrounds, followed by $tt$.   The values of the razor variable cuts were chosen to
maximize the significance, $S/\sqrt{B}$ (calculated for an integrated luminosity
of 3000 fb$^{-1}$), shown in the last column.

@@

For certain values of the
cuts on kinematic variables or the score of the classifier, no events survived
for one or more of the background components. To guard against overly optimistic
estimates of the significance $S/\sqrt{B}$, we set a lower bound of 3 for the
number of Monte Carlo (MC) events after cuts for each background component, corresponding to
the 95\% confidence interval for a Poisson distribution.  \Shufang{SS: Is it 3 MC events, or 3 weighted events after CS values used? Referee comment 10.}

>>>>

The existence of dark matter provides unambiguous evidence of new physics
beyond the Standard Model (SM) of particle physics. Indeed, given that there is
far more dark matter in the Universe than there is baryonic matter, determining
its precise nature is one of the most exciting challenges in particle physics
today.  One promising group of candidates for dark matter is the class of
stable particles known as weakly interacting massive particles (WIMPs). These
particles arise naturally in many extensions of the SM that are motivated by
the need to stabilize the electroweak scale. One of the most heavily studied
extensions is the Minimal Supersymmetric Standard Model (MSSM), which predicts
a `supersymmetric partner', or \emph{superpartner}, for each SM
particle\footnote{For a detailed review of the MSSM, see Ref.
\cite{Martin:1997ns}.}. In the MSSM with \emph{R}-parity conservation, the
lightest supersymmetric partner (LSP) is predicted to be absolutely stable,
making it a good candidate for dark matter. The identity of the LSP is
determined by the mass hierarchy of the superpartners, which in turn depends on
the mechanism of supersymmetry breaking.  However, taking into account
experimental constraints and phenomenological considerations, the neutralino
LSP emerges as the most attractive candidate for WIMP dark
matter.~\cite{Bertone:2004pz}.

 % Why go beyond the MSSM?
Though a natural MSSM spectrum has the potential to tame the hierarchy problem,
it is under siege from recent data from the Large Hadron Collider (LHC)
\cite{Aaboud:2018ujj, Sirunyan:2018vjp}.  A compelling alternative scenario
comes in the form of split supersymmetry (split SUSY) \cite{Wells:2003tf,
ArkaniHamed:2004yi, Giudice:2004tc}. In this scenario, the lightest
superpartners are the fermionic ones, on the scale of 1-10 TeV, while the
scalar superpartners can be much heavier, on the scale of 100 - 1000 TeV. In
exchange for accepting some level of fine-tuning, we obtain numerous benefits,
including the suppression of flavor-changing neutral currents and greater
compatibility with data from CP-violation experiments.  The low lying fermionic
superpartners consist of neutralinos and charginos (collectively known as
electroweakinos), and gluinos. The current LHC search limits on gluinos are
already around 2 TeV for prompt decay and 2.5 TeV for disappearing track
searches~\cite{CMS-PAS-SUS-19-005}. The limits on electroweakinos with
  heavy scalar superparticles, however, are still relatively weak: between 150
  GeV $-$ 1.0 TeV, depending on the neutralino/chargino species, decay modes,
  and their mass splittings~\cite{ATL-PHYS-PUB-2019-022, Sirunyan:2017lae,
    Sirunyan:2018ubx, Aaboud:2018htj, Aaboud:2018zeb, Aad:2019qnd, Aad:2019vvf,
  Aad:2019vnb, Aaboud:2018ngk, Aaboud:2018sua, Aaboud:2018jiw, Aaboud:2017leg,
Aaboud:2017mpt, Aaboud:2017nhr}.  In this paper, we will focus on the discovery
potential of the neutralinos and charginos at a 100 TeV $pp$ collider. {\bf
Can not find Ref. 9}

@@

The optimal search strategy for finding electroweakinos is highly dependent on
their mass spectra \cite{Han:2013kza}. There are phenomenological collider
studies on finding electroweakinos with a small mass splitting of about 0.1 $-$
50 GeV at the LHC~\cite{Giudice:2010wb, Gori:2013ala, Han:2013usa,
Schwaller:2013baa, Baer:2014cua, Han:2014kaa} and at a 100 TeV $pp$
collider~\cite{Low:2014cba, Bramante:2014tba, Berlin:2015aba, Cirelli:2014dsa,
Mahbubani:2017gjh, Mahbubani:2018tin, Fukuda:2017jmk,
Saito:2019rtg, Han:2018wus}. For a 100 TeV $pp$ collider with $30\
\text{ab}^{-1}$ of data, disappearing track search can discover Wino (Higgsino)
LSP with mass up to about 4.7 TeV (1
TeV)~\cite{Low:2014cba, Cirelli:2014dsa, Mahbubani:2017gjh, Saito:2019rtg, Han:2018wus}.
The discovery reaches from monojet, mono-$Z$, and mono-photon searches are weaker:
about 1 TeV (600 GeV) for Wino
(Higgsino)~\cite{Low:2014cba, Cirelli:2014dsa, Mahbubani:2018tin, Han:2018wus}.
For mass splittings of about 20-30 GeV between low-lying neutralinos and
charginos, soft leptons + missing $E_T$ signal can be
used~\cite{Low:2014cba, Bramante:2014tba}.  In addition, weak boson fusion
process can discover a Wino (Higgsino) up to about 1 TeV (530
GeV)~\cite{Cirelli:2014dsa, Berlin:2015aba}.  Note, however,  that in certain
scenarios, light Higgsinos between 75 $-$ 100 GeV are still viable, evading LEP
and LHC constraints \cite{Egana-Ugrinovic:2018roi}.

@@

Searches for pair produced nearly mass-degenerate Higgsinos  have been
performed at ATLAS and CMS for various decay topologies \cite{Aaboud:2018htj,
Sirunyan:2018ubx, Aaboud:2018zeb}.  For neutralino-chargino pair production
with \emph{WZ} and \emph{Wh} topologies, the 95\% C.L. exclusion limits are
about 650 GeV, 490 GeV, and 535 GeV for \emph{WZ}, \emph{Wh} and an equal
mixture of \emph{WZ}+\emph{Wh} topology, with the strongest limits coming from
the multi-lepton searches.  For neutralino pair production with \emph{ZZ, Zh},
and \emph{hh} topologies\footnote{While such searches assume a gravitino LSP
  with Higgsino NLSPs, the limits are still relevant for our Higgsino NLSPs -
  Bino LSP scenario.}, the limits are about 650 $-$ 750 GeV via multi-lepton or
  multi-$b$ jets searches, depending on the decay branching fractions of the
  Higgsino NLSPs.

@@

Table \ref{tab:cc_cutflowtable} shows the cut efficiencies for a representative
signal benchmark point with $\mu =$ 1 TeV and $M_1$ = 25 GeV.   The
cross-sections of the backgrounds are obtained from MadEvent after performing
the MLM matching procedure. Their small size reflects the $m_{\ell\ell}$ and
$\slashed{E}_T$ cuts we imposed at the parton level. For all the benchmark
points, we require a minimum of three background events (at the MC level, i.e.
unweighted) left over after cuts\footnote{\ap{This is inspired by the upper
    one-sided limit for the mean of a Poisson variable given zero observed
    events, for a confidence level of 95\% (see Table 39.3 of
    \cite{PhysRevD.98.030001}), however, it does not reflect it exactly (since
    we required a minimum on unweighted rather than weighted events).  We
    observed that as we generated more unweighted background events, the
    discovery reach of our analysis showed a steady increase. This, combined with the
    fact that we were pushing the limits of our storage and computing capacity
    (we generated $\approx 14$ million $tt$ events and $\approx
    850$K $tbW$ events - both unweighted), lead us to believe that the projected reaches
presented in this paper are conservative ones.}}. We can see that, after
applying our cuts, $tbW$ remains as the dominant backgrounds, followed by $tt$.
The values of the razor variable cuts were chosen to maximize the significance,
$S/\sqrt{B}$ (calculated for an integrated luminosity of 3000 fb$^{-1}$), shown
in the last column.

@@

\st{For certain values of the
cuts on kinematic variables or the score of the classifier, no events survived
for one or more of the background components. To guard against overly optimistic
estimates of the significance $S/\sqrt{B}$, we set a lower bound of 3 for the
number of Monte Carlo (MC) events after cuts for each background component, corresponding to
the 95\% confidence interval for a Poisson distribution.}\Shufang{SS: Is it 3
MC events, or 3 weighted events after CS values used? Referee comment 10.}
\Adarsh{I added a footnote about this - see footnote 5. I think we can remove
this paragraph...}
